# Data Mining with ChIP seq data deposited in GEO

```{r}
#| include: false
library(epiSeeker)
library(yulab.utils)
Biocpkg <- yulab.utils::Biocpkg

```

There are many ChIP seq data sets that have been published and deposited in GEO database. 
We can compare our own dataset to those deposited in GEO to search for significant overlap data. 
Significant overlap of ChIP seq data by different binding proteins may be used to infer cooperative regulation and 
thus can be used to generate hypotheses.

We collect about **17,000** bed files deposited in GEO, user can use `getGEOspecies` to get a summary based on speices.

## GEO data collection

```{r}
#| label: getGEOspecies
#| eval: false
getGEOspecies() |> head()
##                                               species Freq
## 1                     Actinobacillus pleuropneumoniae    1
## 2 Actinobacillus pleuropneumoniae serovar 3 str. JL03    1
## 3                                       Aedes aegypti   11
## 4                                            Anabaena    6
## 5                                 Anolis carolinensis    7
## 6                                   Anopheles gambiae    2
```


The summary can also based on genome version as illustrated below:

```{r}
#| label: getGEOgenomeVersion
#| eval: false
getGEOgenomeVersion() |> head()

##                 organism genomeVersion Freq
## 1    Anolis carolinensis       anoCar2    7
## 2             Bos taurus       bosTau4    2
## 3             Bos taurus       bosTau6   33
## 4             Bos taurus       bosTau7    2
## 5 Canis lupus familiaris       canFam3   10
## 6 Caenorhabditis elegans          ce10  328
```

User can access the detail information by `getGEOInfo`, for each genome version.

```{r}
#| label: getGEOInfo
#| eval: false
hg19 <- getGEOInfo(genome="hg19", simplify=TRUE)
head(hg19)

##     series_id        gsm     organism
## 111  GSE16256  GSM521889 Homo sapiens
## 112  GSE16256  GSM521887 Homo sapiens
## 113  GSE16256  GSM521883 Homo sapiens
## 114  GSE16256 GSM1010966 Homo sapiens
## 115  GSE16256  GSM896166 Homo sapiens
## 116  GSE16256  GSM910577 Homo sapiens
##                                                                                                       title
## 111          Reference Epigenome: ChIP-Seq Analysis of H3K27me3 in IMR90 Cells; renlab.H3K27me3.IMR90-02.01
## 112            Reference Epigenome: ChIP-Seq Analysis of H3K27ac in IMR90 Cells; renlab.H3K27ac.IMR90-03.01
## 113            Reference Epigenome: ChIP-Seq Analysis of H3K14ac in IMR90 Cells; renlab.H3K14ac.IMR90-02.01
## 114                      polyA RNA sequencing of STL003 Pancreas Cultured Cells; polyA-RNA-seq_STL003PA_r1a
## 115          Reference Epigenome: ChIP-Seq Analysis of H4K8ac in hESC H1 Cells; renlab.H4K8ac.hESC.H1.01.01
## 116 Reference Epigenome: ChIP-Seq Analysis of H3K4me1 in Human Spleen Tissue; renlab.H3K4me1.STL003SX.01.01
##                                                                                                     supplementary_file
## 111         ftp://ftp.ncbi.nlm.nih.gov/geo/samples/GSM521nnn/GSM521889/suppl/GSM521889_UCSD.IMR90.H3K27me3.SK05.bed.gz
## 112          ftp://ftp.ncbi.nlm.nih.gov/geo/samples/GSM521nnn/GSM521887/suppl/GSM521887_UCSD.IMR90.H3K27ac.YL58.bed.gz
## 113          ftp://ftp.ncbi.nlm.nih.gov/geo/samples/GSM521nnn/GSM521883/suppl/GSM521883_UCSD.IMR90.H3K14ac.SK17.bed.gz
## 114 ftp://ftp.ncbi.nlm.nih.gov/geo/samples/GSM1010nnn/GSM1010966/suppl/GSM1010966_UCSD.Pancreas.mRNA-Seq.STL003.bed.gz
## 115              ftp://ftp.ncbi.nlm.nih.gov/geo/samples/GSM896nnn/GSM896166/suppl/GSM896166_UCSD.H1.H4K8ac.AY17.bed.gz
## 116       ftp://ftp.ncbi.nlm.nih.gov/geo/samples/GSM910nnn/GSM910577/suppl/GSM910577_UCSD.Spleen.H3K4me1.STL003.bed.gz
##     genomeVersion pubmed_id
## 111          hg19  19829295
## 112          hg19  19829295
## 113          hg19  19829295
## 114          hg19  19829295
## 115          hg19  19829295
## 116          hg19  19829295
```

If _simplify_ is set to _FALSE_, extra information including _source\_name_, _extract\_protocol_, _description_, _data\_processing_ 
and _submission\_date_ will be incorporated.

## Download GEO ChIP data sets

`r Biocpkg("ChIPseeker")` provide function `downloadGEObedFiles` to download all the bed files of a particular genome.

```{r}
#| label: downloadGEObedFiles
#| eval: false
downloadGEObedFiles(genome="hg19", destDir="hg19")
```

Or a vector of GSM accession number by `downloadGSMbedFiles`.
```{r}
#| label: downloadGEObedFiles-vector
#| eval: false
gsm <- hg19$gsm[sample(nrow(hg19), 10)]
downloadGSMbedFiles(gsm, destDir="hg19")
```


## Overlap significant testing

After download the bed files from GEO, we can pass them to `enrichPeakOverlap` for testing the significant of overlap. 
Parameter _targetPeak_ can be the folder, _e.g._ hg19, that containing bed files. `enrichPeakOverlap` will parse the folder and 
compare all the bed files. It is possible to test the overlap with bed files that are mapping to different genome or 
different genome versions, `enrichPeakOverlap` provide a parameter _chainFile_ that can pass a chain file and liftOver the _targetPeak_ 
to the genome version consistent with _queryPeak_. Signifcant overlap can be use to generate hypothesis of cooperative regulation. 
By mining the data deposited in GEO, we can identify some putative complex or interacted regulators in gene expression regulation or 
chromsome remodelling for further validation.