---
output:
  md_document:
    variant: gfm
html_preview: false
---


```{r echo=FALSE, results="hide", message=FALSE}
#library("txtplot")
library("badger")
library("yulab.utils")
```


# epiSeeker: an R package for Annotation, Comparison and Visualization of multi-omics epigenetic data


<!-- r badge_bioc_release("epiSeeker", "green")` 
r badge_devel("YuLab-SMU/epiSeeker", "green")`
[![Bioc](http://www.bioconductor.org/shields/years-in-bioc/epiSeeker.svg)](https://www.bioconductor.org/packages/devel/bioc/html/epiSeeker.html#since)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)


[![platform](http://www.bioconductor.org/shields/availability/devel/epiSeeker.svg)](https://www.bioconductor.org/packages/devel/bioc/html/epiSeeker.html#archives)
[![Build Status](http://www.bioconductor.org/shields/build/devel/bioc/epiSeeker.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/epiSeeker/)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-green.svg)](https://github.com/YuLab-SMU/epiSeeker/commits/master)
-->




```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription('epiSeeker')$Description)
```


## :writing_hand: Authors

Guangchuang YU 

School of Basic Medical Sciences, Southern Medical University

<https://yulab-smu.top>



## :arrow_double_down: Installation

Get the released version from Bioconductor:

```r
## try http:// if https:// URLs are not supported
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
## BiocManager::install("BiocUpgrade") ## you may need this
BiocManager::install("epiSeeker")
```

Or the development version from github:

```r
## install.packages("devtools")
devtools::install_github("YuLab-SMU/epiSeeker")
```


## Contributing

We welcome any contributions! By participating in this project you agree to
abide by the terms outlined in the [Contributor Code of Conduct](CONDUCT.md).

